# Visual Exploratory Analysis of input data

This notebook allows the visual exploration of our input timeseries.
We start by importing libraries and defining paths

```{r}
## Init by deleting all variables and functions
rm(list=ls())
library(stringr)
library(lubridate)
library(knitr)

## Set the working directory. Change this to the location of the root file on the computer. Note that "/" is always used in R, also in Windows
root_directory = "C:/.../fiftyshadesofgrey"
path_out = paste(root_directory, "/data/out/", sep="")
path_in = paste(root_directory, "/data/in/", sep="")

setwd(paste(root_directory, "/src", sep=""))

# Get all input files names
setwd(path_in)
list_file_names <- list.files(pattern = "blg_*")
```


## Utility functions

Here a few utility functions have been defined for plotting.
Reference source: the ctsmr.info website http://ctsm.info/building1.zip


```{r}
setpar <- function(tmpl=NA,...)
{
  ## Get par list
  p <- par(no.readonly=TRUE)
  ## Templates
  if(!is.na(tmpl))
  {
    if(tmpl=="ts")
    {
      par(mfrow=c(3,1),
          oma = c(3,0,2,2),
          mar = c(0,4,0.5,0),
          xaxt = "n",
          mgp = c(2.2,0.4,0),
          tcl = -0.4
      )
    }
    if(tmpl=="pdf")
    {
      par(mar = c(4,4,1,1),
          mgp = c(2.2,0.7,0),
          tcl = -0.4
      )
    }
  }
  ## Replace all the parameters given in prm
  ## Get only the ... parameters
  i <- which(!names(match.call()) %in% names(match.call(expand.dots=FALSE)))
  if(length(i)>0)
  {
    par(...)
  }
  invisible(p)
}

asP <- function(timeVal, tz="GMT", ...)
{
  ## For easy conversion from string or seconds since 1970-01-01 to POSIXct
  switch(class(timeVal[1])[1],
         character=as.POSIXct(timeVal,tz=tz, ...),
         POSIXct=timeVal,
         POSIXlt=timeVal,
         ISOdate(1970,1,1,0)+timeVal
  )
}

asPlt <- function(timeVal, tz="GMT", ...)
{
  ## For easy conversion from string or seconds since 1970-01-01 to POSIXlt
  switch(class(timeVal[1])[1],
         character=as.POSIXlt(timeVal,tz=tz, ...),
         POSIXct=as.POSIXlt(timeVal),
         POSIXlt=timeVal,
         as.POSIXlt(ISOdate(1970,1,1,0)+timeVal)
  )
}

per <- function(tstart,time,tend)
{
  asP(tstart) < time & time <= asP(tend)
}
```

## Visual plot loop

Finaly, we loop over the input files to produce visualizations of our measurement data.

```{r}
### CHOSE FILE
for (file in list_file_names) {
  df <- read.csv(paste(path_in,file,sep=""),sep=";",header=TRUE)
  # Get blg uuid from file name
  split_file_name <- str_split_fixed(file, "_", 2)
  uuid_filtering <- sapply(split_file_name, tail, 1)[[2]]
  uuid_filtering <- str_split_fixed(uuid_filtering, ".csv", 2)[1]
  # Convert to datetime
  df$timedate <- ymd_hms(df$t)
  ## df$t is now hours since start of the experiment.
  df$t <- seq(0, length(df$t)-1, by=1) / 4  # dt = 15 minutes
  
  # Define input X
  X <- df[c("t", "timedate", "Ps", "Ta", "Thm", "yTi", "timedate")]
  # Removing NA values
  X = X[complete.cases(X), ]
  
  
  start_date <- as.Date(X$timedate[1], format='%a %b %d %H:%M:%S UTC %Y')
  
  ## ----plotData, fig.height=6----------------------------------------------
  ## Plot the time series (see "functions/setpar.R" to see the plot setup function)
  setpar("ts", mfrow=c(4,1))
  gridSeq <- seq(asP(toString(start_date)),by="days",len=length(X$t)/4/24)
  ## 
  plot(X$timedate,X$yTi,type="n",xlab="",ylab="yTi")
  abline(v=gridSeq,h=0,col="grey85",lty=3)
  lines(X$timedate,X$yTi)
  ## 
  plot(X$timedate,X$Ta,type="n",xlab="",ylab="Ta")
  abline(v=gridSeq,h=0,col="grey85",lty=3)
  lines(X$timedate,X$Ta)
  ## 
  plot(X$timedate,X$Thm,type="n",xlab="",ylab="Thm")
  abline(v=gridSeq,h=0,col="grey85",lty=3)
  lines(X$timedate,X$Thm)
  ##
  plot(X$timedate,X$Ps,type="n",xlab="",ylab="Ps")
  abline(v=gridSeq,h=0,col="grey85",lty=3)
  lines(X$timedate,X$Ps)
  axis.POSIXct(1, X$timedate, xaxt="s", format="%Y-%m-%d")
}
```